\chapter{Conclusions} % Main chapter title

\label{Chapter6} 

This dissertation consisted in the study of solvation free energy calculations of aromatic solutes in different solvents by using the SAFT-$\gamma$ Mie coarse-grained force field. Solvation free energy studies are mostly done using water as a solvent and with all-atom force fields based on the Lennard-Jones potential. Therefore, with this study, we were able to provide data about the capability of a coarse-grained force field based on the Mie potential in calculating solvation free energies. Additionally, the solvation free energy estimations carried out here can help improve the SAFT-$\gamma$  Mie force field since these calculations are helpful in identifying errors and shortcomings in the modeling process. The SAFT-$\gamma$ Mie uses the SAFT-VR Mie EoS in its parameterization, which results in a relatively straightforward top-down method of obtaining parameters. Following this strategy, the phenanthrene parameters, which were not available in the original database of this force field, were obtained using vapor-liquid equilibrium data and two different ring equations and geometries. However, only the parameters estimated with the ring equation proposed by \citeonline{muller2017} were utilized in the solvation free energy simulations since this equation did not require molecular simulation data in its parameterization.

To perform our expanded ensemble simulations, we optimized the coupling parameters and their respective simulation weights. The resulting potential energies from the expanded ensemble simulations then served as input to estimate solvation free energy differences with the MBAR method. The results for non-aqueous solvents had absolute deviations from the experimental
data of less than 2.0 kcal/mol, except for the pair 1-octanol+anthracene. We also observed the geometry effect on the free energy curves - larger molecules had steeper curves and more substantial absolute deviations. The influence of carbon dioxide on the solvation free energy of phenanthrene in toluene was found to be negligible according to the SAFT-$\gamma$ Mie force field. 

Hydration free energy calculations with the SAFT-$\gamma$ Mie model required the use of relatively large values of $k_{ij}$ to produce satisfactory results. We chose to estimate the parameter with the output from molecular dynamics data since the strategy of using the SAFT-VR Mie EoS provided high absolute deviations from the experimental data. This necessity of one additional parameter probably happens due to the lack of a term to account for the hydrogen bond in the EoS on which this force field is based and due to problems associated with the coarse-graining of water molecules. The results obtained with $k_{ij}$ estimated with MD output were satisfactory, the absolute deviations from the experimental data found were smaller than the ones for the GAFF and ELBA force fields. We also used the solvation free energies to calculate partition coefficients in water/1-octanol and water/hexane. The obtained absolute deviations from experimental data were similar to the ones found for all-atom force fields (GROMOS, TraPPE and OPLS-AA/TraPPE) and another coarse-grained force filed (ELBA).

Overall, the SAFT-$\gamma$ Mie force field proved to be a suitable model to represent the solvation phenomenon of non-aqueous solvents. It correctly described solvation free energies of solutes mimicking asphaltenes dissolved in hexane, toluene, 1-octanol. However, the calculation of hydration free energies required the use of a binary interaction parameter estimated with MD output, which increased the simulation time significantly. This fact evidenced flaws in the methodology used by the SAFT-$\gamma$ force field and raised questions about the feasibility of this model for hydration free energy calculations. Nevertheless, the SAFT-$\gamma$ Mie force field for water used here does not predict freezing at room temperature as other force fields do, which is essential for our hydration free energy calculations. Therefore, it would be relevant to test if the binary interaction parameter for our aromatic solutes estimated here can be used in hydration free energy calculations of other aromatic solutes and if we could use MBAR to obtain the $k_{ij}$ through reweighting. Hence, we would only need to carry out molecular dynamics simulations with one value of $k_{ij}$, and then use this output to estimate with MBAR the results with other $k_{ij} 's $. We also have some ideas that could be developed in the future using the results from this dissertation. The SAFT-$\gamma$ Mie force field could be used to model larger asphaltene models and, consequently, increase the scale of the simulations we performed. Additionally, it would be a valid investigation to study new methodologies to calculate solubility with solvation free energies using the SAFT-$\gamma$ Mie force field.


