\chapter{Methodology} % Main chapter title

\label{Chapter4} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\section{Phenanthrene Parameterization}

\section{Solvation Free energy Calculations}
The molecular dynamic simulations were done to estimate the free energy differences. The Lammps package \cite{lammps}  was used to perform this simulations with the velocity-Verlet algorithm \cite{verlet} to integrate the motion's equation with a time step of 1 fs. The simulations were carried out with the Lammps user package for alchemical simulations developed by our group, available at https://github.com/atoms-ufrj/USER-ALCHEMICAL, to perform expanded ensemble simulations with the Mie potential since the Lammps package. The molecules were treated as rigid bodies except the ones with $m_{s}=1$. The thermostat was the one described by \citeonline{kamberaj} with a damping factor of 100 fs and the barostat was the Nose/Hoover with chains with a damping factor of 1000 fs. The SAFT-$\gamma$ Mie model doesn't consider electrostatics interactions explicitly, hence there was no shifting of forces or long range corrections and the potential cutoff was equal to 20 $\dot{A}$ with a neighbor skin of 2 $\dot{A}$. The initial configuration of the  solvated system was generated with the Packmol package \cite{packmol} . For the binary mixtures, one molecule of solute and a varying number of solvent molecules- 700 molecules for toluene and octanol, 1024 for hexane, 3000 for water - were randomly added to a cubic box. The simulations to study solvation free energy of phenanthrene in a mixture of toluene and carbon dioxide were done with different fractions of carbon dioxide. The system consisted of one molecule of phenanthrene for all the fractions and  72 molecules of $CO_{2}$ and 652 molecules of toluene for $x_{CO_{2}} = 0.1$; 123 molecules of $CO_{2}$ and 618 molecules of toluene for $x_{CO_{2}} = 0.166$; 166 molecules of $CO_{2}$ and 589 molecules of toluene for $x_{CO_{2}} = 0.22$; 232 molecules of $CO_{2}$ and 545 molecules of toluene for $x_{CO_{2}} = 0.299$.
All simulations were carried out at 298 K and 1 bar, except the ones containing carbon dioxide. These were performed at 298 K and at the pressure of the liquid phase equilibrium correspondent to the $CO_{2}$ fraction \cite{co2toliq} . For each simulation, the initial box was equilibrated at the NPT ensemble for 2 ns and then the resulting configurations were used as an input for the expanded ensemble simulations. Trial simulations were done on the expanded ensemble with the purpose of obtaining the values of the weights and the optimal values of lambda as described above. Theses simulations were shorter, lasting around 2 ns, and the first group of lambda used for all the pairs solvent-solute was: (0.0,0.15,0.2,0.25,0.3,0.4,0.45,0.5,0.55,0.7,0.9,1.0). The first trial weights were set to zero or they were given the values of the weights found for similar mixtures. With the values of the weights and the $\lambda $ defined for each mixture, larger simulations with an equilibration time of 1 ns and production time of at least 15 ns were performed. Lastly, we applied the MBAR method and the tools of the software alchemical-analysis \cite{klimovich} on the equilibrated data to effectively calculate and analyze the free energy of solvation.